### 2021-09-13 plos_latex_template.tex
simple comments in the 2nd role by Batool

Nevertheless, having a diverse offer of networking opportunities that can appeal to people with different backgrounds, accessibility needs, and preferences can be challenging, especially if you have the mindset of organizing each activity for the complete pool of  attendants. If you think of smaller activities that can reach specific groups, preferably co-lead by community leaders, this sessions can be more productive and successful, and even inclusive, than trying to organize one single activity that can please the whole community. Some examples are the newbies sessions for first timers, mixers lead by Rladies or MiR, or a leisure activity that reunites subgroups with the same interests: arts, exercise, sports, movies, etc.

Adopting a code of conduct and creating a team to enforce it are key aspects in creating a safe environment during a conference \cite{favaroYourScienceConference2016}. The code of conduct is a document meant to keep the community safe and should state clearly: the unacceptable behaviors, the spaces of the conference in which it applies, the consequences for engaging in unacceptable behavior, and the way to report violations \cite{aurora2019}. 
The code of conduct should be displayed prominently in several spaces of the conference to deter people from unacceptable behavior. An efficient code of conduct acts as a protection for the community because the people who are the target of unacceptable behavior tend to be the ones with less power or privilege.

The code of conduct team should receive training on how to receive reports, respond to incidents, and communicate their responses. A diverse code of conduct team will be more understanding of power dynamics and sensitive to discrimination and harassment issues. We strongly recommend reading “How to Respond to Code of Conduct Reports” \cite{aurora2019} as an excellent starting point for the Code of Conduct team work. A Code of Conduct response committee needs to be trained and prepared in advance on how to decide on the incident reports.

>>>>

Nevertheless, having a diverse offer of networking opportunities that can appeal to people with different backgrounds, accessibility needs, and preferences can be challenging, especially if you have the mindset of organizing each activity for the complete pool of  attendants. If you think of smaller activities that can reach specific groups, preferably co-lead by community leaders, this sessions can be more productive and successful, and even inclusive, than trying to organize one single activity that can please the whole community. Some examples are the newbies sessions for first timers, mixers lead by R-Ladies or MiR, or a leisure activity that reunites subgroups with the same interests: arts, exercise, sports, movies, etc.

Adopting a code of conduct and creating a team to enforce it are key aspects in creating a safe environment during a conference \cite{favaroYourScienceConference2016}. The code of conduct is a document meant to keep the community safe and should state clearly: the unacceptable behaviors, the spaces of the conference in which it applies, the consequences for engaging in unacceptable behavior, and the way to report violations \cite{aurora2019}. 
The code of conduct should be displayed prominently in several spaces of the conference to deter people from unacceptable behavior, which includes microaggression. An efficient code of conduct acts as a protection for the community because the people who are the target of unacceptable behavior tend to be the ones with less power or privilege.

The code of conduct team should receive training on how to receive reports, respond to incidents, and communicate their responses. A diverse code of conduct team will be more understanding of power dynamics and sensitive to discrimination and harassment issues. There are also disciplinary cultures and geographical considerations that may need to be considered when developing and communicating the code of conduct (CoC). We strongly recommend reading “How to Respond to Code of Conduct Reports” \cite{aurora2019} as an excellent starting point for the Code of Conduct team work. A Code of Conduct response committee needs to be trained and prepared in advance on how to decide on the incident reports.
